Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
revisions to the abstract and keywords

\title{Analyzing the impact of social attributes on the success of commit integration}
%Or some better name, Zack can probably think of a better one, he is good with names

@@

\begin{abstract}
Software quality is an important and desirable aspect of the software 
development process overall, especially with the increasing participation of a very
diverse pool of developers, the number of commits and pull requests keeps increasing 
and the mechanisms available to identify which developers are pushing high 
quality commits and pull requests is scarce.
Recent research has explored how the open source community manages
this question finding that both technical and social factors are factors in 
the success of project contributions on GitHub.  
This investigation defined a successful project contribution as a project
contribution that gets
accepted to the project. However, with continuous integration, we can
explore this question a step further.  We can better estimate the success of a
contribution by investigating if the contribution passed all the quality standards set 
by the repository owners.  We performed an initial investigation into the technical and
social factors involved in a commit that successfully passes the integration
tests. Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We have found that while social factors cause a noticeable increase
in predictive power (12\%), further investigation into these factors are
required.
\end{abstract}

\begin{IEEEkeywords}
Social Attributes; Travis CI; Github; Social Networks; Predicting Integration 
Success; Social Coding
\end{IEEEkeywords}

>>>>

\title{Analyzing the impact of social attributes on commit integration success}
%Or some better name, Zack can probably think of a better one, he is good with names
%ZC- Haha thanks.  I'm starting to lean to very descriptive titles now.  They
%are nice for searching.

@@

\begin{abstract}
Software quality is an important and desirable aspect of the software 
development process. 
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing.
As the number of commits and pull requests increase, it becomes more difficult
to only accept quality contributions.
Recent research has explored how the open source community manages
this question, finding that both technical and social factors are factors in 
the success of project contributions on GitHub.  
However, with continuous integration, we can
explore this question a step further.  We can better estimate the success of a
contribution by investigating if the contribution passed all the quality standards set 
by the repository owners.  We performed an initial investigation into the technical and
social factors involved in a commit that successfully passes the integration
tests. Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We have found that while social factors cause a noticeable increase
in predictive power (12\%), further investigation into these factors are
required.
\end{abstract}

\begin{IEEEkeywords}
Social Attributes; Travis CI; GitHub; Social Networks; Predicting Integration 
Success; Social Coding
\end{IEEEkeywords}
